### 2012-02-04 sermons/Revelation1:1-3.tex
Sermon update.

\subsection{He is the Savior}
\I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
                in His own blood, \ldots}
\I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
                I am alive forevermore.}
\I Rev 5:6 \Q{And I looked, and behold, in the midst of the throne
                and of the four living creatures, and in the midst of the
                elders, stood a Lamb as though it had been slain, \ldots}
\I Rev 13:8 \Q{All who dwell on the earth will worship him [the beast], 
                whose names have not been written in the Book of Life
                of the Lamb who was slain from the foundation of the world.}
\I Rev 5:9 \Q{``You are worthy to take the scroll, \\
                And to open its seals; \\
                For You were slain, \\
                And have redeemed us to God by Your blood \\
                Out of every tribe and tongue and people and nation, \ldots''}
\I Rev 5:12 \Q{``Worthy is the Lamb who was slain \\
                To receive power and riches and wisdom, \\
                And strength and honor and glory and blessing!''}
\I Rev 5:13 \Q{``Blessing and honor and glory and power \\
                Be to Him who sits on the throne, \\
                And to the Lamb, forever and ever!''}
\I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
                the Root of David, has prevailed to open the scroll 
                and to loose its seven seals.''}
\I Rev 3:7 \Q{``He who has the key of David, He who opens and no one shuts, 
                and shuts and no one opens.''}
\I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
\I Rev 19:7 \Q{``Let us be glad and rejoive and give Him glory,
                for the marriage of the Lamb has come,
                and His wife has made herself ready.''}
\I Rev 7:17 \Q{``for the Lamb who is in the midst of the throne 
                will shepherd them and lead them to living fountains of waters.
                And God will wipe away every tear from their eyes.''}
\I Rev 21:22-23 \Q{But I saw no temple in it, for the Lord God Almighty 
                and the Lamb are its temple. The city had no need 
                of the sun or of the moon to shine in it, 
                for the glory of God illuminated it. The Lamb is its light.}
\I Rev 22:1-2 \Q{And he showed me a pure river of water of life, 
                clear as crystal, proceeding from the throne of God 
                and of the Lamb. In the middle of its street, and on either
                of the river, was the tree of life, which bore twelve fruits,
                each tree yielding its fruit every month. 
                The leaves of the tree were for the healing of the nations.}
\I Rev 22:3-4 \Q{And there shall be no more curse, but the throne of God
                and of the Lamb shall be in it, and His servants shall 
                serve Him. They shall see His face, and His name shall be on
                their foreheads.}

@@

\subsection{His servants}
\subsection{Things which must shortly take place}
\section{The Authority of the Revelation of Jesus Christ}
\subsection{The word of God}
\subsection{The testimony of Jesus Christ}
\subsection{All things that he saw}

>>>>

\subsection{He is the Savior}
\I Rev 1:5 \Q{To Him who loved us and washed us from our sins 
                in His own blood, \ldots}
\I Rev 1:18 \Q{I am He who lives, and was dead, and behold, 
                I am alive forevermore.}
\I Rev 5:6 \Q{And I looked, and behold, in the midst of the throne
                and of the four living creatures, and in the midst of the
                elders, stood a Lamb as though it had been slain, \ldots}
\I Rev 13:8 \Q{All who dwell on the earth will worship him [the beast], 
                whose names have not been written in the Book of Life
                of the Lamb who was slain from the foundation of the world.}
\I Rev 5:9 \Q{``You are worthy to take the scroll, \\
                And to open its seals; \\
                For You were slain, \\
                And have redeemed us to God by Your blood \\
                Out of every tribe and tongue and people and nation, \ldots''}
\I Rev 5:12 \Q{``Worthy is the Lamb who was slain \\
                To receive power and riches and wisdom, \\
                And strength and honor and glory and blessing!''}
\I Rev 5:13 \Q{``Blessing and honor and glory and power \\
                Be to Him who sits on the throne, \\
                And to the Lamb, forever and ever!''}
\I Rev 5:5 \Q{``Do not weep. Behold, the Lion of the tribe of Judah,
                the Root of David, has prevailed to open the scroll 
                and to loose its seven seals.''}
\I Rev 3:7 \Q{``He who has the key of David, He who opens and no one shuts, 
                and shuts and no one opens.''}
\I Rev 1:18 \Q{``And I have the keys of Hades and of Death.''}
\I Rev 19:7 \Q{``Let us be glad and rejoice and give Him glory,
                for the marriage of the Lamb has come,
                and His wife has made herself ready.''}
\I Rev 7:17 \Q{``for the Lamb who is in the midst of the throne 
                will shepherd them and lead them to living fountains of waters.
                And God will wipe away every tear from their eyes.''}
\I Rev 21:22-23 \Q{But I saw no temple in it, for the Lord God Almighty 
                and the Lamb are its temple. The city had no need 
                of the sun or of the moon to shine in it, 
                for the glory of God illuminated it. The Lamb is its light.}
\I Rev 22:1-2 \Q{And he showed me a pure river of water of life, 
                clear as crystal, proceeding from the throne of God 
                and of the Lamb. In the middle of its street, and on either
                of the river, was the tree of life, which bore twelve fruits,
                each tree yielding its fruit every month. 
                The leaves of the tree were for the healing of the nations.}
\I Rev 22:3-4 \Q{And there shall be no more curse, but the throne of God
                and of the Lamb shall be in it, and His servants shall 
                serve Him. They shall see His face, and His name shall be on
                their foreheads.}

@@

\subsection{His servants}
\I If you are a Christian, then you are the target audience of Revelation.
    This highlights our need, as His servants, to know His Revelation.
\BI \I Not for the world, but for His saints.
    \I Not primarily for evangelism, but for the edification of the Church.
    \I Not for repentance in the unbeliever, but in the life of the Christian.
\EI
\I This need is further deepened when we consider that 
    ``servant'' is more accurately translated ``slave''.
\BI \I We are the property of Jesus Christ,
    \I owned by Him,
    \I fully subject to His will.
    \I Jesus has the full and complete rights to your life. \EI
\I This means that knowing Revelation 
\BI \I Is not a matter of leisure, or a hobby -- 
        it is a matter of necessity and duty, as Christ's slave.
    \I It is not about enriching yourself, 
        or simply becoming more knowledgeable about the Bible -- 
        it's about being faithful, and obedient.\EI
\I Revelation is \emph{literally} Master Jesus' final instructions 
    to His slaves before His return.
\I And we cannot be the
\BI \I faithful and wise servant (Matt 24:45) who is found faithfully
        carrying out his Master's instructions, or
    \I the servant (Matt 25) who has faithfully used the 2 or 5
        talents entrusted to him by his Master \EI
    apart from knowing and obeying the Revelation of Jesus Christ.

\subsection{Things which must shortly take place}
\I \emph{Transition:} We must make Revelation an urgent, \#1 priority,
    because it informs us of the imminent.
\I If imminent back then, how much more so now!
\I Revelation has \emph{not} been fulfilled:
\BI \I We are not in the new heaven and the new earth.
    \I Death and Hades have not been thrown into the lake of fire.
    \I Sin has not been abolished.
    \I There still remains the final battle against Satan and the world.
    \I The final judgement of sinners and the righteous.
    \I Christ's evaluation of believers. \EI
\I These things are future, but not far off, they are future imminent.
\BI \I The Lord is not slow, He is merciful (2 Peter 3:19)
    \I Nothing is hard for Him, 
        but His judgement would have been far too much for you to bear! \EI
\I The Second Coming is unheralded, it comes without warning.
\BI \I Rev 22:7, 12 \Q{``Behold! I am coming quickly!''}
    \I Rev 16:15 \Q{``Behold! I am coming as a thief''} \EI
\I We must learn from the flood of Noah's time (Matt 24:38-39).
    \Q{``For as in the days before the flood, they were eating and drinking,
    marrying and giving in marriage, until the day that Noah entered
    the ark, and did not know until the flood came and took them all away,
    so also will the coming of the Son of Man be.''} 
\I We must be those who are prepared for His return 
    (Matt 25, parable of the virgins).
\I And we can start on this by reading, understanding, and obeying
    the Revelation of Jesus Christ.

\section{The Authority of the Revelation of Jesus Christ}
\subsection{The word of God}
\subsection{The testimony of Jesus Christ}
\subsection{All things that he saw}
